Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-06 WSSSPE3/report/WSSSPE3_review.tex
add Abigail's talk

\item \textbf{Abigail Cabunoc Mayes, Bill Mills, Arliss Collins and Kaitlin
Thaney: \textit{Collaborative Software Development as Sustainable Software: Lessons
from Open Source}}

>>>>

\item \textbf{Abigail Cabunoc Mayes, Bill Mills, Arliss Collins and Kaitlin
Thaney: \textit{Collaborative Software Development as Sustainable Software: Lessons
from Open Source}}
Abigail Cabunoc Mayes combines two properties of open source that, together,
form a suitable habitat for sustainable software. The first of the two
properties, being public, does not only mean public code. It also includes
public discussions, a public process of including contributions, and an open
license. The second property, participatory, stresses the importance of
reaching out to the community and helping potential new members by providing
better documenation and learning experiences, like code review and examples of
good first bug reports. Together, Abigail concludes, these two properties not
only lead to higher quality, reusability and ease of understanding, but
eventually, to sustainablity.
